---
title: "che"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{che}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Working example of using Convex Hull Ensembles and range bagging with the `che` package
## Matt Hill 2019

```{r setup}
library(che)
library (raster)
library (maptools)
library (rgeos)

# simple world outline from maptools package
data("wrld_simpl")
```

## this data is the in the `che` package - will implement neater soon....
```{r}
load("../data/insect_dist.Rdata")
```

## Bioclim data
```{r}
bioclimall <- raster::getData('worldclim', var='bio', res=2.5)
```


# Background creation

## Native range for this species is South Africa
```{r}
e <- extent (10, 40, -35, -15)
SAfrica <- crop (bioclimall, e)
#convert to a stack
SAfrica <- stack(unstack(SAfrica))
```

## Species data

### Halotydeus destructor
```{r fig.width=5, fig.height=5}
dist <- insect_dist[insect_dist$Species =="h_destructor" & insect_dist$Range == "Native",]

sp_df <- cbind(as.data.frame(dist[,c("Longitude", "Latitude")]),raster::extract(SAfrica, as.data.frame(dist[,c("Longitude", "Latitude")])))
plot (SAfrica[[1]])
points(as.data.frame(dist[,c("Longitude", "Latitude")]), pch=20)
```

## Biomes

The biomes are available as a shapefile from WWF
```{r}

if (!file.exists("official/wwf_terr_ecos.shp")){
  temp <- tempfile()
  download.file("https://c402277.ssl.cf1.rackcdn.com/publications/15/files/original/official_teow.zip",temp)
  unzip(temp)
  unlink(temp)
}
terres <- readShapePoly("official/wwf_terr_ecos.shp")
```


## Create a raster using biomes and native range points

Using the `che::background_builder` function to set up sampling environment

```{r fig.width= 5, fig.height=5}
clim <- cbind(as.data.frame(dist[,c("Longitude", "Latitude")]),raster::extract(SAfrica, as.data.frame(dist[,c("Longitude", "Latitude")])))

nat_ras <- background_builder(distrib=clim, 
                              terres=terres,
                              wrld_simpl= wrld_simpl, 
                              ref_rast = bioclimall[[1]])

plot (nat_ras)
```

Using the `che::prepare_data` function to prepare the data for the modelling process
```{r}

model.data <- prepare_data(rasters=bioclimall, mask_raster=nat_ras, predict.to=SAfrica, 
             spp.dist=clim[,1:2], w.val=1.e-6, bg.sample = 50000)
```

## Parallel processing of GAMs
```{r}

model.out <- che_model(spp = "h_destuctor", parallel = TRUE, model.data=model.data)


```
## Reconcile outputs

```{r fig.width= 5, fig.height=5}

q_CHE <- che_out(model.out, 0.25)

```

```{r}
hist(q_CHE$AUC.scores)
abline(v=q_CHE$AUC.thresh, col="red")
```
```{r}

library(tmap)
library (classInt)
library (viridis)


c_dist <- dist[,2:3]
coordinates(c_dist) <- ~Longitude+Latitude

tm_shape(q_CHE$predicted)+
  tm_raster(palette=viridis(10), n=10,
            style="pretty", title="Suitability")+
  tm_shape(wrld_simpl)+
  tm_borders(col="grey60", lwd=2)+
  tm_shape(c_dist)+
  tm_dots(size=0.3, col="red")+
  tm_layout(legend.position=c("right", "BOTTOM"))
```

